---
title: 'Homework #6'
author: "Carter Athens"
date: "4/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Import the data and clean appropriately. To read in the data, you can use `readxl::read_xlsx('fileNameHere', sheet='sheetNameHere')`. Required data are in the sheets `Best in show` and `Best in show full sheet`. Take extra care on the column names and the first few rows of the data frame after read in.
```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)

bestDog <- readxl::read_xlsx('KIB - Best in Show (public).xlsx', sheet = 'Best in show full sheet', skip = 2) %>% select(Breed = `Sources - see bottom right`, 'Type of dog' = `category`, 'Size of dog' = `size category`, Score = `ULTIMATE TOP DOG MEGA SCORE`, Popularity = `POPULAR RATING`, Trainability = `1 INTELLIGENCE (TRAINABILITY) ranking`)

bestDog[bestDog == 'no data'] <- NA

bestDog <- bestDog %>% mutate('Type of dog' = as.factor('Type of dog'), Trainability = as.numeric(Trainability), 'Size of dog' = as.factor('Size of dog'))

bestDog$Size <- factor(bestDog$'Size of dog', levels(bestDog$'Size of dog')[c(1, 2, 3)])

bestDog <- bestDog[-c(1), ]

#bestDog$Trainability[bestDog$Trainability <= 40] <- 0
#bestDog$Trainability[bestDog$Trainability > 40] <- 1
#bestDog <- bestDog %>% subset(Trainability <= 1) #This command just subsets all of the trainability rows with a numeric variable, getting rid of the NA values which makes the plot cleaner

#bestDog <- bestDog %>% mutate(Trainability = as.factor(Trainability))
```

2. Create a graphics similar to the  [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/) figure. Your figure need to display the following information with appropriate plotting elements:

- breed of dog
- type of dog (work, toy, etc.)
- size of dog
- data score 
- popularity
- intelligence of the dog
- appropriate legends & explanation

```{r}


```

Hints and Notes:

- The breed of dog can be displayed without the silhouttes (text only is fine)
- Avoid (too much) overlap!
- Choose a good color scheme.
- Your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. 